Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-07-17 GNproof.tex
few more thoughts

Next we prove the base case of $l=1$. Else, let $q \in Q_1 \setminus Q_0$. By construction $q$ shares support with a propagators in $\Q_{0}$. Call this propagator $p_r$. By the above, $p_r \in \cP_{m-1}$. Suppose that $q \not \in \cP_{m-1}$. The violet note above implies that $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.  If $a_j = j_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$). Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction. There are two types of propagators in $Q_1 \setminus Q_0$, the $q$ such that $j_m$ is inside $q$ in the $a_q-1$ ordering, and the $q$ where $j_m$ is on the outside.

Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$. If this set is empty, we are done. Otherwise, let $q \in Q_l \setminus Q_{l-1}$. By construction $q$ shares support with a propagator in $Q_{l-1}$. Call this propagator $p_r$. Let $v_r$ be the fourth vertex of $p_r$ in the $a_{r}-1$ ordering. Since $I_i(p_r) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$. We have two cases: there exists a $p_s \in Q_{l-2}$ such that both $p_r$ is on the inside in the $a_s -1$ ordering, and $j_m$ is on the outside, or $p_r$ is on the outside of any $p_s \in Q_{l-2}$ that has $j_m$ on the outside in the $a_s-1$ ordering. In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_s$ in the $a_{s}-1$ ordering.  Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_s < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction. \sanote{I think this takes care of the picture you sent last night. However, it doesn't address your original complaint about the second case.}

Consider the second case ($a_j-1 < j_m < v_j$). As above, $q$ shares support with $p_j$. More specifically, $a_j \in V(q)$. By construction, $p_r$ must share support with some $p_s \in Q_{l-2}$.

\begin{figure}[h]
\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$. Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
\end{figure} \sanote{This can't happen. $a_j \in V(q)$ by construction}

>>>>

Next we prove the base case of $l=1$. Else, let $q \in Q_1 \setminus Q_0$. By construction $q$ shares support with a propagators in $\Q_{0}$. Call this propagator $p_r$. By the above, $p_r \in \cP_{m-1}$. Suppose that $q \not \in \cP_{m-1}$. The violet note above implies that $q$ must be inside $p_r$ in the $a_{r}-1$ ordering.  If $a_r = r_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$). Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction. There are two types of propagators in $Q_1 \setminus Q_0$, the $q$ such that $j_m$ is inside $q$ in the $a_q-1$ ordering, and the $q$ where $j_m$ is on the outside.

Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$. If this set is empty, we are done. Otherwise, let $q \in Q_l \setminus Q_{l-1}$. By construction $q$ shares support with a propagator in $Q_{l-1}$. Call this propagator $p_r$. Let $v_r$ be the fourth vertex of $p_r$ in the $a_{r}-1$ ordering. Since $I_i(p_r) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$. We have two cases: there exists a $p_s \in Q_{l-2}$ such that both $p_r$ is on the inside in the $a_s -1$ ordering, and $j_m$ is on the outside, or $p_r$ is on the outside of any $p_s \in Q_{l-2}$ that has $j_m+1$ on the outside in the $a_s-1$ ordering. In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_s$ in the $a_{s}-1$ ordering.  Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_s < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction. \sanote{I think this takes care of the picture you sent last night. However, it doesn't address your original complaint about the second case.}

In the second case, if $p_r$ is on the outside of all $p_s \in Q_{l-2}$ that has $j_m+1$ on the outside in the $a_s-1$ ordering. {\color{violet}I worry that as soon as we have propagators ``escaping'' $j_m$, i.e. having an endpoint in the cyclic intervale $[j_m+1, i-1]$, we start having to include propagators on ``the wrong side'' of the diagram. Which is why I don't like this case.}

\begin{figure}[h]
\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$. Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step} 
\end{figure} \sanote{in both these pictures, you would have to have some chain of propagators coming out from $j_m$ to meet $p_s$ and then you have a crossing of propagators issue. $p_r$ must be on the outside of $p_s$}
